{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-09-08 wacv_for_review.tex
Burak Final Edit Before Submission

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. On the other
hands, a translation filter, $R_{t}^{L}$, is designed to look at a
larger search area to estimate the target's translation and recover
from any potential drifts. Another translation filter, $R_{t}^{S}$, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the main idea behind the KCF.

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of 
the activations of $2^{th}$, $2^{th}$ and $4^{th}$ convolutional layer features
of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
since it provides higher spatial resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed to address specific challenges in single, target
tracking problem. Thus each of them should have different values for
the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates ($\beta$) of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned
to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
$R_{s}$. For our particle filter implementation, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples}, ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a pre-defined
threshold.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column flipped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection module
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

\textbf{Evaluation on Particle Filter Contribution} For the $UAV123$
dataset, we also evaluated the performance of the {\it E}nKCF with and
without the particle filter. In particular, we use 50 sequences
labeled as no abrupt camera motion in the dataset. To evaluate the
robustness of particle filter, we add noise, drawn from a uniform
distribution ($[-20,20]$), to the translation estimations of the
KCFs. In these setup, the {\it E}nKCF with particle filter achieves
$51.98\%$ precision ($20$px), outperforming the one without particle
filter {\it E}nKCF by $6.32\%$. Thus, with the removal of global
camera motion, the integration of particle filter into the {\it E}nKCF
as shown in Figure \ref{Workflows} further improved the results.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows
Deep{\it E }nKCF's performance on UAV123 Dataset. Deep{\it
  E}nKCF outperformed the {\it E}nKCF with hand-crafted features
by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success
rates (AUC). The \textit{conv224-VGG} setting performed slightly
better than \textit{conv222-VGG} in precision while achieving similar
success rate (AUC) indicating that higher level feature abstraction
works better for the smaller ROIs. By using feature abstractions
from the VGGNet pre-trained on millions of images, we can better represent
the low level features of the object than hand-crafted features
in challenging cases such as low contrast ROIs. However, the contribution 
of the deep features is constrained by two factors : (1) low spatial resolution in deeper layers and (2) 
lost targets due to large target and camera motion in the UAV123 dataset.

>>>>

In summary, the scale filter, $R_{s}$, is designed to directly handle
the scale change of a target and provides $R_{t}^{L}$ and $R_{t}^{S}$
with more focused ROIs about the target's translation. On the other
hand, a translation filter, $R_{t}^{L}$, is designed to look at a
larger search area to estimate the target's translation and recover
from any potential drifts. Another translation filter, $R_{t}^{S}$, is
designed to addresses the drawback of $R_{t}^{L}$ that it may learn
noisy shape features due to its large search area. In what follows, we
will detail the main idea behind the KCF.

@@

There has been a large volume of studies on utilizing a pre-trained
CNN features to tracking-by-detection algorithms. For example,
\cite{danelljan2015convolutional} used the activations of the first
and second convolutional layer of the VGGNet \cite{simonyan2014very}.
They report that the first convolutional layer features lead to
slightly better precision and success rates than the second layer due
to lost spatial information this layer. \cite{ma2015hierarchical}
proposed a KCF tracker integrating features with higher abstraction
capacity.  Their method first employs the third convolutional layer
features to estimate the response map. In the next stage, the KCF,
concentrating on the second convolutional layer features, is run to
update transition. The third KCF then works on the transition given by
the previous KCF and learns the first convolutional layer features to
update the transition. This coarse-to-fine approach accommodates
different levels of abstractions of the object. However, it runs
multiple KCFs in a sequential fashion, increasing the run-time
complexity. For this reason, we follow a similar approach to
\cite{danelljan2015convolutional} to embed deep features in {\it
  E}nKCF. Our {\it E}nKCF framework enables us to exploit different
level of feature encodings with different KCFs. The translation
filters, $R_{t}^{L}$ and $R_{t}^{S}$, consider at least twice bigger
area than the scale filter, $R_{s}$. Given this, we can assign deeper
feature encodings to $R_{s}$ as it learns less spatial information
than $R_{t}^{L}$ and $R_{t}^{S}$. Thus we assign the activations of
the fourth convolutional layer features ($26\times26\times128$) to
$R_{s}$ whereas $R_{t}^{L}$ and $R_{t}^{S}$ are assigned the
activations of the second layer features
($109\times109\times64$). Figure \ref{fig:Filters_CNN} illustrates
this feature assignment. Additionally, we assign the second
convolutional layer features to $R_{s}$ as in $R_{t}^{L}$ and
$R_{t}^{S}$ and compare this setting (\textit{conv222-VGG}) to
\textit{conv224-VGG}. The conv222 setting stands for the assignment of 
the activations of $2^{th}$ convolutional layer features
of VGGNet to $R_{t}^{L}$, $R_{t}^{S}$ and $R_{s}$. We use the VGGNet 
since it provides higher spatial resolution at the first several layers than AlexNet
\cite{krizhevsky2012imagenet}.

@@

\textbf{Finding Optimal Hyper-parameters} Each of three KCFs in {\it
  E}nKCF is designed to address specific challenges in single target
tracking problem. Thus each of them should have different values for
the optimal parameters. For instance, the primary task of the
translation filter, $R_{t}^{L}$ is to estimate the translation of a
target from the previous frame whereas the scale filter, $R_{s}$ and
the estimated state of the particle filter are primarily used to
estimate the scale and translation. Because of this, we set the
learning rates of individual filters, $R_{t}^{L}$,
$R_{t}^{S}$, and $R_{s}$ differently as $0.020$, $0.020$ and
$0.010$. For the kernel of the Gaussian neighboring function, we
empirically found the optimal values of $\alpha$ as $0.7$, $0.6$, and
$0.9$ for $R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$. We set the scale
filter update threshold, $T_{R_{s}}$, to 4, peak-to-sidelobe (PSR)
ratio. Finally, the padding size for the correlation filters is tuned
to $3$ for $R_{t}^{L}$, $2.50$ for $R_{t}^{S}$, and $1$ for
$R_{s}$. For our particle filter implementation, we empirically set
the number of particles to $1000$ to balance the run-time performance
and accuracy. To keep the level of variance among the particles
reasonable, we performed the re-sampling only when the
\textit{efficient number of samples}, ($ \hat{N}_{eff} \approx
(\sum_{p=1}^{P}w_{p}^{2})^{-1} $), is lower than a pre-defined
threshold.

@@

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column flipped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection module
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{t}^{L}$ and $R_{S}$
at every frame, but this combination decreases run-time
performance to 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.

\textbf{Evaluation on Particle Filter Contribution} For the UAV123
dataset, we also evaluated the performance of the {\it E}nKCF with and
without the particle filter. In particular, we use 50 sequences
labeled as no abrupt camera motion in the dataset. To evaluate the
robustness of particle filter, we add noise, drawn from a uniform
distribution ($[-20,20]$), to the translation estimations of the
KCFs. In these setup, the {\it E}nKCF with particle filter achieves
$51.98\%$ precision ($20$px), outperforming the one without particle
filter {\it E}nKCF by $6.32\%$. Thus, with the removal of global
camera motion, the integration of particle filter into the {\it E}nKCF
as shown in Figure \ref{Workflows} further improved the results.

@@

Figure \ref{fig:UAV123_DATASET_DeepFeatures} shows
DeepE{\it n}KCF's performance on UAV123 Dataset. Deep{\it
  E}nKCF outperformed the {\it E}nKCF with hand-crafted features
by about $3\%$ to $5\%$ in precision (20 px) and $2\%$ in success
rates (AUC). The \textit{conv224-VGG} setting performed slightly
better than \textit{conv222-VGG} in precision while achieving similar
success rate (AUC) indicating that higher level feature abstraction
works better for the smaller ROIs. By using feature abstractions
from the VGGNet pre-trained on millions of images, we can better represent
the low level features of the object than hand-crafted features
in challenging cases such as low contrast ROIs. However, the contribution 
of the deep features is constrained by two factors : (1) low spatial resolution in deeper layers and (2) 
lost targets due to large target and camera motion in the UAV123 dataset.
